---
title: "Who Does More Pushups"
author: "Carlos Fajardo"
date: "11/25/2020"
output:
html_document:
number_sections: true
toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
data("pushups")
```

# Introduction
$H_0$: There is no difference between the average number of pushups of line vs skill players  

$H_A$: The average number of pushups done by line players is statistically different than that of skill players  

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

# Methods
by examining the variables we observed the problems type is numerical - categorical so we will upload the support file from rmd.temp  

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
plot(pushups~position,data=pushups)
```

Visually observing the boxplot the upper limit of the player is close tot the bottom 25% of the skill player and they can do much more than the line players.

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
favstats(pushups~position,data=pushups)
```

We see the mean of the line players is 17 and that the mean of skill player is 49 which is about three times as big.  

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
t.test(pushups~position,data=pushups)
```

the p-value is 0.000009421 is a very small number and this is way smaller than 0.05. Therefore we reject the null hypothesis.  

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

When your markdown file successfully knits and you are satisfied with your results, then push your work back to your github repository and submit the link to your github repo to canvas  to complete this assignment.